---
title: "Analysis"
output:
  html_document:
    df_print: paged
---

##### ISSP, Social Inequality, Cumulation (1987, 1992, 1999, 2009 & 2019)

The data are worked up in the article: 

Breznau, Nate, Lisa Heukamp, Hung HV Nguyen, and Tom Knuf. 2024. “The Moderating Role of Government Heuristics in Public Preferences for Redistribution.” Journal of European Social Policy 09589287241290742. doi: 10.1177/09589287241290742.

This was forked from https://github.com/hungnguyen167/Social-Status

```{r , include=FALSE}
library(pacman)
pacman::p_load("tidyverse", 
               "jtools",
               "lme4",
               "report")

knitr::opts_chunk$set(message = F, warning = F)

```


```{r }

df_na <- readRDS(here::here("data", "df_na.RDS"))
#df_macro <- readRDS(here::here("data", "df_macro.RDS"))



```

### Within and Between

Setup a dataset that defines within- and between-variables

```{r }

df_na <- df_na %>%
  group_by(iso3c) %>%
  mutate(govreduce_b = mean(gov_redist, na.rm = T), # gov should reduce diffs
         govreduce_w = gov_redist - govreduce_b,
         incdiff_b = mean(incdiff, na.rm = T), # differences in income too large
         incdiff_w = incdiff - incdiff_b,
         gini_disp_b = mean(gini_disp, na.rm = T), # Solt
         gini_disp_w = gini_disp - gini_disp_b,
         gov_corrupt_percept = cpi_ii, #Corruption Perceptions Index
         gov_no_confidence = noconf_govZ_i) %>% # WVS confidence in gov
  ungroup()

```


## Regressions

This interacts perceptions of corruption with the within-country (over time) gini (m1) and the confidence in government variable from the World Values Survey aggregated by country-year (m2)

```{r}

m1 <- lmer(govreduce_w ~ gini_disp_w*gov_corrupt_percept + (1 | iso3c), data = df_na)

m2 <- lmer(govreduce_w ~ gini_disp_w*gov_no_confidence + (1 | iso3c), data = df_na)

export_summs(m1, m2)

```



## References

```{r cite}
report::cite_packages()
```


## Colophon

```{r colophon}
sessionInfo()
```